---
title: "Canadian Beach Cohort Study"
author: "Ian Young"
date: "`r Sys.Date()`"
format: 
  pdf
editor: visual
---

```{r}
#| echo: false
pacman::p_load(
  rio,
  here,
  tidyverse,
  gtsummary,
  rstatix, 
  janitor, 
  flextable
)

load("G:/My Drive/Research/Projects-TMU/Beach water illness/CIHR Beach Cohort Study/Analysis_beach_cohort_study/.RData")
```

As of `r Sys.Date()`, we have recruited `r num_participants` individual participants from `r num_households` households (mean household size = `r house_size`). Of these participants, `r num_participants-num_unique_participants` participated in the study more than once. A summary of participant responses is highlighted below.

Among `r num_eligiblehouse_follow` households and `r num_eligible_follow` individual participants that have completed the beach survey 7 or more days ago (and have had an opportunity to complete the follow-up), the **individual participant response rate** is `r response_rate`%.

### Recruitment Stats by Beach

```{r}
#| echo: false
data |> group_by(beach) |> select(beach, date, house_id) |> 
   summarize(Num_households = n_distinct(house_id),
             Num_participants = n(), 
             Num_days = n_distinct(date),
             Participants_per_day = round(Num_participants/Num_days, digits = 1))
```

## Recruitment Stats by Weekends/Holidays vs. Weekdays

```{r}
#| echo: false
data |> group_by(weekend_holiday) |> select(date, weekend_holiday, house_id) |> 
  summarize(Num_households = n_distinct(house_id),
            Num_participants = n(), 
            Num_days = n_distinct(date),
            Participants_per_day = round(Num_participants/Num_days, digits = 1))
```

## Sociodemographics

```{r}
#| echo: false
data |> 
  select(age1, gender, education2, residence, ethnicity) |> 
  tbl_summary(digits = list(all_categorical() ~ c(0, 1))) |> 
  as_flex_table() 
```

## Baseline health and beach activities

```{r}
#| echo: false
data |>
  select(base_agi, base_resp, base_ear, base_eye, base_skin, cond_GI, cond_resp, cond_skin,
         cond_allergy, cond_immune, cond_none, prev_act1, beach_exp_algae,
         beach_exp_sunscreen, beach_exp_repellent, beach_exp_food) |> 
  tbl_summary(digits = list(all_categorical() ~ c(0, 1))) |> 
  as_flex_table() 
```

## Water and sand exposures

```{r}
#| echo: false
data |> 
  select(water_contact, water_act_swim, water_act_surf, water_act_kite, water_act_wind,
         water_act_wake, water_act_ski, water_act_paddle, water_act_snorkel, water_act_dive,
         water_act_wade, water_act_sail, water_act_boat, water_act_fish, water_act_canoe,
         water_act_kayak, water_act_other, water_exp_body, water_exp_head, water_exp_mouth, 
         sand_contact, sand_mouth1, sand_act_dig, sand_act_bury) |> 
  tbl_summary(digits = list(all_categorical() ~ c(0, 1))) |> 
  as_flex_table() 
```

## E. coli Levels by Recruitment Date

```{r}
#| echo: false
#| warning: false
data |>
  ggplot(aes(x = date, y = e_coli)) +
  geom_point(colour = "black") + 
  geom_line(colour = "steelblue") + 
  theme_minimal() +
  labs(y = "E. coli geometric mean (CFU / 100 mL)", x = "Recruitment date")
```

## Illness Outcomes (Excluding those with Baseline Symptoms)

```{r}
#| echo: false
data_follow |> 
  select(agi3, respiratory3, ear_infection3, eye_infection3, skin_infection3, illness_any) |> 
  tbl_summary(digits = list(all_categorical() ~ c(0, 1))) |> 
  as_flex_table() 
```

## AGI Severity

```{r}
#| echo: false
data_follow |>
  filter(agi3 == "Yes") |> 
  select(misswork, misswork_days, med_antibiotics, med_otc, med_none, healthcare1,
         blood_stool1, stool_test1, emergency, hospital) |> 
  tbl_summary(digits = list(all_categorical() ~ c(0, 1))) |> 
  as_flex_table() 
```

## Outcomes by Water and Sand Exposure Status - excluding those with same outcomes at baseline

#### Any Water Contact

```{r}
#| echo: false
data_follow |> 
  select(agi3, respiratory3, ear_infection3, eye_infection3, skin_infection3, illness_any,
         water_contact) |> 
  tbl_summary(by = water_contact, digits = list(all_categorical() ~ c(0, 1))) |> 
  as_flex_table() 
```

#### Any Sand Contact

```{r}
#| echo: false
data_follow |> 
  select(agi3, respiratory3, ear_infection3, eye_infection3, skin_infection3, illness_any,
         sand_contact) |> 
  tbl_summary(by = sand_contact, digits = list(all_categorical() ~ c(0, 1))) |> 
  as_flex_table() 
```

## Household Follow-up Contact Preference

```{r}
#| echo: false
data |> distinct(house_id, preference) |>
  select(preference)  |> 
  tbl_summary(digits = list(all_categorical() ~ c(0, 1))) |> 
  as_flex_table() 
```

## Compare Sociodemographics of those who Completed Follow-up Survey vs. Not

```{r}
#| echo: false
data |> mutate(follow_date = Sys.Date()-date) |> 
  filter(follow_date >=8) |> 
  select(age1, gender, education2, residence, ethnicity, base_agi,
         base_resp, base_ear, base_eye, base_skin, water_contact, water_act_swim,
         water_act_wade, water_exp_body, water_exp_head, water_exp_mouth, sand_contact,
         sand_act_dig, sand_act_bury, sand_mouth1, follow)  |> 
  tbl_summary(by = follow, digits = list(all_categorical() ~ c(0, 1))) |> 
  as_flex_table() 
```
